Sampling Strategies in Decisions from Experience

### 2021-11-27 manuscript.Rmd
Use papaja package to format the document as APA7 style manuscript

---
title: 'Sampling Strategies in Decisions from Experience'
author: "Linus Hof, Thorsten Pachur, Veronika Zilker"
bibliography: references_sampling-in-dfe.bib
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
    fig_width: 10
    fig_height: 7
csl: apa.csl
editor_options: 
  markdown: 
    wrap: sentence
  chunk_output_type: console
---

@@

# Introduction

@@

# Sampling in Decisions from Experience

@@

cpt_long %>% 
  filter(parameter == "gamma" | parameter == "delta") %>% 
  ggplot(aes(x = s, y = mean)) +
  geom_density_2d_filled(contour_var = "ndensity") + 
  scale_fill_scico_d(palette = "buda") +
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
  labs(x ="Switching Probability",
       y = "Parameter Value",  
       fill="Density") + 
  facet_grid(parameter~a) + 
  theme_minimal()
```

>>>>

---
title             : "Sampling Strategies in Decisions from Experience"
shorttitle        : "Sampling in Decisions from Experience"

header-includes: 
  - \renewcommand\author[1]{}
  - \renewcommand\affiliation[1]{}
  - \authorsnames[1, 2, 2]{Linus Hof, Thorsten Pachur, Veronika Zilker}
  - \authorsaffiliations{{Department of Psychology, Heidelberg University}, {Center for Adaptive Rationality, Max Planck Institute for Human Development}}

author: 
  - name          : "Linus Hof"
    affiliation   : "1"
    corresponding : yes    
    address       : "Department of Psychology, Heidelberg University, Hauptstraße 47-51, 69117 Heidelberg, Germany"
    email         : "linushof@posteo.de"
    role:
      - Conceptualization
      - Methodology
      - Formal Analysis
      - Visualization
      - Software
      - Validation
      - Writing---original draft
  - name          : "Thorsten Pachur"
    role:
      - Conceptualization
      - Methodology
      - Supervision
  - name          : "Veronika Zilker" 
    role:
      - Conceptualization
      - Methodology
      - Supervision

note: | 
  Unsubmitted draft

authornote: |
 This is a dynamic document which can be reproduced from the accompanying GitHub repository: https://github.com/linushof/sampling-in-dfe. This version was created from the commit with the hash ``r repro::current_hash()``.

abstract: |
  Add abstract

keywords          : ""
wordcount         : ""

bibliography      : ["references_sampling-in-dfe.bib"]
csl               : apa.csl

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
linkcolor         : "blue"
mask              : no
draft             : no

classoption       : "man"
documentclass     : "apa7"
output            : papaja::apa6_pdf
---

@@

@@

@@

cpt_long %>% 
  filter(parameter == "gamma" | parameter == "delta") %>% 
  ggplot(aes(x = s, y = mean)) +
  geom_density_2d_filled(contour_var = "ndensity") + 
  geom_density_2d(contour_var = "ndensity") +
  scale_fill_scico_d(palette = "buda") +
  scale_color_scico_d(palette = "buda") + 
  scale_x_continuous(breaks = seq(0, 1, .2)) + 
  scale_y_continuous(limits = c(0,2), breaks = seq(0, 2, .2)) +
  labs(x ="Switching Probability",
       y = "Parameter Value",  
       fill="Density") + 
  facet_grid(parameter~a) + 
  theme_minimal()
```
